Modular Verification Using Extended Finite Automata

### 2006-03-10 doc/EFA/efa.tex
*** empty log message ***

In the last two steps  of the algorithm we obtain a monolithic description of $A_e$. To avoid the so called
 state-space explosion problem, we must investigate the modular automata model obtained in step 2. However,
 the modular structure in the algorithm does not have the correct alphabet and can therefore not be used to
 verify specifications against a given plant model. For instance, suppose we have a model of the plant and
 a specification in EFA form. To analyze the specification against the plant and at the same time
use the modular structure in the translation algorithm we must translate them simultaneously.

@@

The synchronous composition of two EFA's must consider that the automata
may have both events and variables in common. When synchronizing two automata
$A_e=\langle Q^A, \Sigma^A, \delta^A_e, q^A_i, Q^A_m,
X^A, G^{A}, x^{A}_0, X^{A}_m \rangle$ and $B_e=\langle Q^B, \Sigma^B,
\delta^B_e, q^B_i, Q^B_m, X^B, G^{B}, x^{B}_0, X^{B}_m \rangle$ that have
common variables one must check that $A_e$ and $B_e$ are
consistent. First of all, the common variables must have the same
initial values. Secondly, we require that the action functions
triggered by a common enabled event $\sigma\in \Sigma_{A}\cap
\Sigma_{B}$ in the two automata update common variables to the
same values, i.e. if the $i^{ith}$ variable in $x^{A}$ and the
$j^{ith}$ variable in $x^{B}$ are the same then $(a_{q^A \sigma}(x^{A}))_i = (a_{q^B
\sigma}(x^{B}))_j$. However, if the corresponding guard
formula is false it may happen that $a_{q^A \sigma p^A}(x^{A}))_i \neq (a_{q^B
\sigma p^B}(x^{B}))_j$ even though the two automata are consistent.
To avoid such situations we require that action functions of common
variables are identical.

>>>>

In the last two steps  of the algorithm we obtain a monolithic description of $A_e$. To avoid the so called
 state-space explosion problem, we must investigate the modular automata model obtained in step 2. However,
 the modular structure in the algorithm does not have the correct alphabet and can therefore not be used to
 verify specifications against a given plant model. For instance, suppose we have a model of the plant and
 a specification in EFA form. To analyze the specification against the plant and at the same time
use the modular structure in step 2 in the translation algorithm we must translate the
specification and the plant simultaneously.

Before we calculate a supervisor from the modular model obtained in step 2 we divide the alphabet of $A'$ (the
relabelled alphabet)
into as many subsets as the number of events (events that occur in transitions) in $A_e$. Each subset
$\Sigma_\sigma=\{\text{events in } A' \text{ obtained by relabelling } \sigma \}$
is an equivalence class representing the event $\sigma$ in the original alphabet. The supervisor
calculated from the modular model with the relabelled alphabet have one important restriction,
 it must either accept all events in an equivalence class or forbid all events in an equivalence class. Of course
  we need only to consider the controllable events in $A_e$.
 The key is to treat all the relabelled events as uncontrollable and control them
 simultaneously with the original controllable event
 of $A_e$ that defines the their equivalence class. This
 can easily be obtained using regular algorithms by adding a simple automata shown in fig.

@@

The synchronous composition of two EFA's must consider that the automata
may have both events and variables in common. When synchronizing two automata
$A_e=\langle Q^A, \Sigma^A, \delta^A_e, q^A_i, Q^A_m,
X^A, G^{A}, x^{A}_0, X^{A}_m \rangle$ and $B_e=\langle Q^B, \Sigma^B,
\delta^B_e, q^B_i, Q^B_m, X^B, G^{B}, x^{B}_0, X^{B}_m \rangle$ that have
common variables one must check that $A_e$ and $B_e$ are
consistent. First of all, the common variables must have the same
initial values. Secondly, we require that the action functions
triggered by a common enabled event $\sigma\in \Sigma_{A}\cap
\Sigma_{B}$ in the two automata update common variables to the
same values, i.e. if the $i^{ith}$ variable in $x^{A}$ and the
$j^{ith}$ variable in $x^{B}$ are the same then $(a_{q^A \sigma}(x^{A}))_i = (a_{q^B
\sigma}(x^{B}))_j$. However, if the corresponding guard
formula is false it may happen that $a_{q^A \sigma p^A}(x^{A}))_i \neq (a_{q^B
\sigma p^B}(x^{B}))_j$ even though the two automata are consistent.
To avoid such situations we require that action functions of common
variables are identical?
